A Study of Residual Adapters for Multi-Domain Neural Machine Translation

### 2020-08-16 2020/wmt_20/emnlp2020.tex

\subsection{Varying the positions and number of residual adapters}

Tables~\ref{tab:performance-en-fr-pos-reg} and \ref{tab:performance-en-de-pos-reg} report the BLEU scores for 6 domains in each language pair: \domain{med},\domain{law},\domain{bank},\domain{talk},\domain{it} and \domain{rel} for En$\rightarrow$Fr; \domain{gov}, \domain{eco}, \domain{tour}, \domain{bank}, \domain{med} and \domain{news} for En$\rightarrow$De. We first see that for the latter direction, the basic version \system{Res-Adap} also outperforms the \system{mixed} baseline on average, with large gains for the small domains \domain{tour}, \domain{bank} and comparable results for the other domains.
% in almost all domains while stays equivalent to the baseline in \domain{med} in En$\rightarrow$Fr and \domain{news}, \domain{gov}, \domain{eco}, \domain{med} in En$\rightarrow$De.
   %    However, \system{FT-full} still remains the best model for all test domains.
\fyFuture{Full FT for en->DE ? }

@@

% which covers a wide range in the hierarchy of attention layers. To observe how much the number of residual adapters affects the performance of the adapted model. By the limit of computation resources, we limit our study to the case of 3 adapters at positions: 2,4,6 in each side of the NMT model. By doing this, we could cover 3 situations: 1 adapter (mentioned in the previous paragraph), 3 adapters and 6 adapters (in the normal setting) in each side (encoder and decoder).\fyTodo{We have 12 layers, have we not ?}

%  In most cases, the performance increases with respect to the number of residual adapters used in architecture. The setting \system{FT-block} using residual adapters at all levels outperforms setting \system{Res-Adap$_{(2,4,6)}$} using residual adapter at 3 levels, which outperforms \system{Res-Adap$_{(2)}$}, \system{Res-Adap$_{(4)}$} , \system{Res-Adap$_{(6)}$} using residual adapter at only one level. However, the difference in performance between positions is not significant except the case of domain \domain{rel} (En-Fr) in which the lower position shows the lower performance.\fyDone{What does bold mean ?}\fyDone{Number of parameters ?}

>>>>

\subsection{Varying the positions and number of residual adapters}
Tables~\ref{tab:performance-en-fr-pos-reg} and \ref{tab:performance-en-de-pos-reg} report the BLEU scores for 6 domains in each language pair: \domain{med},\domain{law},\domain{bank},\domain{talk},\domain{it} and \domain{rel} for En$\rightarrow$Fr; \domain{gov}, \domain{eco}, \domain{tour}, \domain{bank}, \domain{med} and \domain{news} for En$\rightarrow$De. We first see that for the latter direction, the basic version \system{Res-Adap} also outperforms the \system{mixed} baseline on average, with large gains for the small domains \domain{tour}, \domain{bank} and comparable results for the other domains.
% in almost all domains while stays equivalent to the baseline in \domain{med} in En$\rightarrow$Fr and \domain{news}, \domain{gov}, \domain{eco}, \domain{med} in En$\rightarrow$De.
   %    However, \system{FT-full} still remains the best model for all test domains.
\fyFuture{Full FT for en->DE ? }

@@
